Discriminative Sensing Based on Signal Processing for Information Security Analysis

### 2017-11-15 docs/thesis/chapters/5_conclusion_future_work/conclusion.tex
chapter 2 ok
tensor-dl and spell check

In the context of anomaly-based schemes, this thesis proposed a statistical approach based on signal processing techniques for detection of malicious traffic in computer networks. The proposed technique is based on eigenvalue analysis, model order selection (MOS) and eigen similarity analysis, where MOS and eigenvalue analysis are applied to detect time frames under attack. In addition, we evaluated the accuracy and performance of the proposed framework applied to a experimental scenario and to the DARPA 1998 dataset.

@@

Finally, we proposed a fraud detection approach composed by tensor-based dictionary learning for discriminant analysis of a mobile payment dataset.

@@

The incremental individualized approach of eigen similarity analysis, is able to detect low similarity for all evaluated scenarios and types of network attack, while the other approaches present false positives or low sensibility to eigen similarity analyis for network attack detection. Therefore, the incremental individualized approach is able to gradually and incrementally adapt to network traffic changing, preserving the sensibility to identify outliers or anomalies by time or network port, and reducing the occurrence of false positives.

@@

As prove of concept, a fully working mobile application was developed to test the proposed security solution and acquired results provide evidence that besides achieving the desired security features, the solution also has positive results in terms of performance. This fact is due to the usage of lightweight operations and the optimized combination of the selected security methods. The proposed approach is a practical application to be used in the corporate mobile environment. It is implemented as a fully working mobile client and can be used for any type of enterprise. Also, part of concept is seed for new security solutions for big data apps.

@@

We attempt to analyse the processing capacity problem of measurement of distributed systems through network traffic analysis, the results of the work presented in this thesis provide the contributions below:

\begin{enumerate}
	\item We proposed an approach based on eigen similarity analysis for extracting detailed information about accurate time and network ports under network attack, and evaluated the accuracy and performance of the proposed framework applied to a experimental scenario and to the DARPA 1998 dataset;
	\item We discussed the computational complexity of the proposed framework and evaluated the required processing time for tested scenarios;
	\item We proposed an architechture and techniques for offline behavioral analysis of a corporate mobile client security architecture;
	\item We discussed the processing time of the proposed framework for mobile devices;
	\item We proposed an tensor-based dictionary learning approach for fraud detection in mobile payment transactions;
	\item We published the following papers reporting our results:
	\begin{enumerate}
		\item T. P. B. Vieira, D. F. Ten\'orio, J. P. C. L. da Costa, E. P. de Freitas, G. Del Galdo, and R. T. de Sousa J\'unior, \textit{Model Order Selection and Eigen Similarity based Framework for Detection and Identication of Network Attacks}. Journal of Networking and Computer Applications (JNCA), Vol 90, Jul 2017, Pages 26–41 \cite{vieira2017model}.
		\item T. Galibus, T. P. B. Vieira, E. P. de Freitas, R. Albuquerque, J. P. C. L. da Costa, R. T. de Sousa Jr, V. Krasnoproshin, A. Zaleski, H. Vissia, and G. del Galdo, \textit{Offline Mode for Corporate Mobile Client Security Architecture}. Mobile Networks and Applications, Springer, Mar 2017, Pages 1-17 \cite{galibus2017offline}.
		\item K. H. C. Ramos, R. T. Sousa Jr, T. P. B. Vieira, and J. P. C. L. da Costa, \textit{Discovering Critical Success Factors for Information Technologies Governance through Bibliometric Analysis of Research Publications in This Domain}. Information (Yamaguchi), 2016 \cite{ramos2016information}.
		\item K. H. C. Ramos, T. P. B. Vieira, J. P. C. L. da Costa, and R. T. Sousa Jr., \textit{ANÁLISE MULTIDIMENSIONAL DE FATORES CRÍTICOS DE SUCESSO EM GOVERNANÇA DE TI NA ADMINISTRAÇÃO PÚBLICA FEDERAL À LUZ DOS DADOS DE CONTROLE EXTERNO}. in Proc. 12th International Conference on Management of Technology and Information Systems (CONTECSI), 2015, São Paulo, Brazil \cite{}.
	\end{enumerate}
\end{enumerate}

@@

\begin{itemize}
	\item Improvements for obtaining better false positive rates, as well as for make the proposed framework able to identify sparse probe attacks or subtle behaviors, such as exfiltration or covert communication, considering the evaluation of a flow-based analysis and novel datasets;
	\item Distributed or parallel processing can also be evaluated to analyze the scalability and processing capacity for monitoring high thoughput network traffic;
	\item Evaluate the application of the proposed approach to different attack types and domains, considering cases that are aware to behavioral analysis;
	\item Explore enhancements in the analytics methods as well as to extended the approach to be used by mobile devices with even more severe resources constraints;
\end{itemize}

>>>>

In the context of anomaly-based schemes, this thesis proposed a statistical approach based on signal processing techniques for detection of malicious traffic in computer networks. The proposed technique is based on eigenvalue analysis, model order selection (MOS) and eigen similarity analysis, where MOS and eigenvalue analysis are applied to detect time frames under attack. In addition, we evaluated the accuracy and performance of the proposed framework applied to an experimental scenario and to the DARPA 1998 dataset.

@@

Finally, we proposed a fraud detection approach composed by tensor-based dictionary learning for discriminant analysis of a mobile payment dataset, where the problem of imbalanced data is discussed and it is presented one analysis regarding the classification accuracy of the proposed approach against well known classifiers.

@@

The incremental individualized approach of eigen similarity analysis, is able to detect low similarity for all evaluated scenarios and types of network attack, while the other approaches present false positives or low sensibility to eigen similarity analysis for network attack detection. Therefore, the incremental individualized approach is able to gradually and incrementally adapt to network traffic changing, preserving the sensibility to identify outliers or anomalies by time or network port, and reducing the occurrence of false positives.

@@

As prove of concept, a fully working mobile application was developed to test the proposed security solution and acquired results provide evidence that besides achieving the desired security features, the solution also has positive results in terms of performance. This fact is due to the usage of lightweight operations and the optimized combination of the selected security methods. The proposed approach is a practical application to be used in the corporate mobile environment. It is implemented as a fully working mobile client and can be used for any type of enterprise. Also, part of concept is seed for new security solutions for big data applications.

This thesis shows that a tensor-based approach can be used for fraud detection from mobile money transactions, with average results when compared to well known classifiers in one scenario with highly skewed datasets.

@@

We analyze problems related to detection of information security issues and propose new approaches to improve malicious behavior detection through signal processing techniques. The results of the work presented in this thesis provide the following contributions:

\begin{enumerate}
	\item We proposed an approach based on eigen similarity analysis for extracting detailed information about accurate time and network ports under network attack, and evaluated the accuracy and performance of the proposed framework applied to an experimental scenario and to the DARPA 1998 dataset;
	\item We discussed the computational complexity of the proposed framework and evaluated the required processing time for tested scenarios;
	\item We proposed an architecture and techniques for offline behavioral analysis of a corporate mobile client security architecture;
	\item We discussed the processing time of the proposed framework for mobile devices;
	\item We proposed a tensor-based dictionary learning approach for fraud detection in mobile payment transactions;
	\item We published the following papers reporting our results:
	\begin{enumerate}
		\item T. P. B. Vieira, D. F. Ten\'orio, J. P. C. L. da Costa, E. P. de Freitas, G. Del Galdo, and R. T. de Sousa J\'unior, \textit{Model Order Selection and Eigen Similarity based Framework for Detection and Identication of Network Attacks}. Journal of Networking and Computer Applications (JNCA), Vol 90, Jul 2017, Pages 26–41 \cite{vieira2017model}.
		\item T. Galibus, T. P. B. Vieira, E. P. de Freitas, R. Albuquerque, J. P. C. L. da Costa, R. T. de Sousa Jr, V. Krasnoproshin, A. Zaleski, H. Vissia, and G. del Galdo, \textit{Offline Mode for Corporate Mobile Client Security Architecture}. Mobile Networks and Applications, Springer, Mar 2017, Pages 1-17 \cite{galibus2017offline}.
		\item K. H. C. Ramos, R. T. Sousa Jr, T. P. B. Vieira, and J. P. C. L. da Costa, \textit{Discovering Critical Success Factors for Information Technologies Governance through Bibliometric Analysis of Research Publications in This Domain}. Information (Yamaguchi), 2016 \cite{ramos2016information}.
		\item K. H. C. Ramos, T. P. B. Vieira, J. P. C. L. da Costa, and R. T. Sousa Jr., \textit{ANÁLISE MULTIDIMENSIONAL DE FATORES CRÍTICOS DE SUCESSO EM GOVERNANÇA DE TI NA ADMINISTRAÇÃO PÚBLICA FEDERAL À LUZ DOS DADOS DE CONTROLE EXTERNO}. in Proc. 12th International Conference on Management of Technology and Information Systems (CONTECSI), 2015, São Paulo, Brazil \cite{}.
	\end{enumerate}
\end{enumerate}

@@

\begin{itemize}
	\item Improvements for obtaining better false positive rates, as well as for make the proposed framework able to identify sparse probe attacks or subtle behaviors, such as exfiltration or covert communication, considering the evaluation of a flow-based analysis and novel datasets;
	\item Distributed or parallel processing can also be evaluated to analyze the scalability and processing capacity for monitoring high throughput network traffic;
	\item Evaluate the application of the proposed approach to different attack types and domains, considering cases that are aware to behavioral analysis;
	\item Explore enhancements in the analytics methods as well as to extended the approach to be used by mobile devices with even more severe resources constraints;
\end{itemize}

### 2017-11-15 docs/thesis/chapters/appendix/b_pca_svm_cfa/pca_svm_cfa.tex
introducion...
tensor-dl and spell check

\chapter{Critical Success Factor Analysis Based on Feaure Selection}
\label{ch:b_csf_fs}

Critical Success Factor (CSF) is a management term for an element that is necessary for an organization or project to achieve its mission. CSFs represent the principal assets or areas that must be given investments to achieve better results. CSF analysis is one challenger strategic management tool, wich can provide a robust and very practical assessment for strategic planners.

The identification of the most significative information for one problem is referred to as feature selection by the signal processing and data mining areas, as well as it can be formulated as a principal component problem, which is a widely adopted signal processing technique for data visualization and feature extraction. Feature selection aims to select a subset of relevant information from a larger dataset, in order to improve: data visualization and data understanding, storage requirements, dimensionality, processing time, discriminative sensing, and to overcome overfitting problems to improve prediction and classification performance \cite{chandrashekar2014survey}.

Recursive Feature Elimination (RFE) is a feature selection method for small sample classification problems. RFE seeks to improve generalization performance by recursivelly removing the least significant features whose deletion will have the least effect on training errors, according to the higher variance measured from the features \cite{chen2007enhanced}.

We propose a critical factors analysis based on Principal Compoment Analytis (PCA) for visual discriminant analysis and based on RFE combined with Support Vector Machine (SVM) \cite{hearst1998support}, applied to the survey that evaluates the IT governance of brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Results show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, wich are similar to CSFs previsously identified by a qualitative analysis of the same datased.

@@

The brazilian Federal Court of Accounts (TCU, in Portuguese) surveys data regarding IT practices of brazilian public organizations in order to audit IT governance. The dataset with a consolidate view about the answers for this surgey the IT governance index is called iGovTI. The iGovTI is composed by 201 multiple choice questions, used for ranking according to their IT governance, submmited to 349 organizations. The TCU computes the IT governance index and classifies the IT governace of each organization. Additionally, Ramos \emph{et al} \cite{ramos2016information} classifies each question regarding its relevance for IT governance through a qualitative analysis, and identify the CSFs for selected IT managers regarding IT governance.

@@

PCA is a statistical technique commonly used for signal denoising, blind source separation, data compression, data visualization, feature extraction and dimensionality reduction, where a reduced number of features is extrated retaining as much information as possible \cite{jolliffe1986principal}. It uses an orthogonal transformation to convert a set of correlated variables into a set of linearly uncorrelated variables, where the first principal components have the largest variance.

PCA is an orthogonal basis transformation into new basis, by diagonalizing the centered covariance matrix of a data set \{$\mathbf{x}_j \in \mathbb{R}^m, j = 1, ... ,n$\}, defined by $\mathbf{C} = \frac{\mathbf{X}^\intercal\mathbf{X}}{n}$, where $\mathbf{X} = (\mathbf{x}_1, ... , \mathbf{x}_n)^\intercal$ and the samples are assumed to have zero mean. The eigenvectors $\mathbf{v}_i$ of $\mathbf{C}$ are called principal components (PC), and the sample variance along $\mathbf{v}_i$ of $\mathbf{C}$ is given by the corresponding eigenvalue $\lambda_i$. Projecting onto the eigenvectors with the largest eigenvalues assumes that minimal information is lost, considering that in many applications these directions contain the most interesting information, such as in in data compression and de-noising.

Initially, we compute the covariance matrix $\mathbf{C}$ of a zero mean data and visualize the data relationship for the sambple covariance. Sample covariance is calculated by computing deviations of each measurement from the average of all measurements for that variable. Then the deviations for the two measurements are multiplied together separately for each subject. Finally these values are averaged. After that, the eigenvectors $\mathbf{v}_i$ and eigenvalues $\lambda_i$ of $\mathbf{C}$ are computed through Singular Value Decomposition (SVD), then it is possible to evaluate the variance distribution of the extracted components through an empirical cumulative distribution function (ECDF). Evaluating the variance distribution we expect to visualize if some features concentrates the variance and indicates advantages for dimensionality reduction.

@@

Feature selection aims the identification of the most significative information for one problem or algorithm, such as classification or prediction problems. RFE is a feature selection method for small sample classification problems by recursivelly removing the least significant features whose deletion will have the least effect on training errors, according to the higher variance measured from the features through a selected classifier.

Initially, it is necessary to identify one classifier that can identify the iGovTI classificatin of one organization according to a trainning dataset. Therefore, we propose an algorithm evaluatio in order to identify wich one presents the best accuracy for iGovTI classification. The selected algorithm should be used by RFE to identify the CSF, that should be compared to results of the CSF qualitative analysis conducted by Ramos \emph{et al} \cite{ramos2016information}.

Feature selection doesn't combine attributes, as PCA, but just evaluates their informative quality, predictive power and select the best set. Given an external estimator or classifier, that assigns weights to features, RFE is able to select features by recursively considering smaller and smaller sets of features. First, the estimator is trained on the initial set of features and the importance of each feature is obtained either through a coefficient attribute or through a feature importances attribute. Then, the least important features are pruned from current set of features. That procedure is recursively repeated on the pruned set until the desired number of features to select is eventually reached. RFE can also rank all features areaccording to when they were eliminated.

@@

In this section we present the experiements and results for the visual discriminant analysis based on PCA and for CSF analysis based on RFE, and discuss the results.

For the visual discriminant analysis we initially we compute the zero mean and the the covariance matrix $\mathbf{C}$ is computed from $\mathbf{X}$.The resuls are shown by Figure \ref{fig:ch2_fig1}.

@@

In the next step the eigenvectors $\mathbf{v}_i$ and eigenvalues $\lambda_i$ of $\mathbf{C}$ are computed through SVD. Considering that the first principal components have the largest variance indicated by their eigenvalues, it is necessary to evaluate the variance distribution of the measured eigenvalues. Therefore, we present the Figure \ref{fig:ch2_fig2}, wich shows the variance ECDF of the iGovTI questions and shows that 97\% of the questions have variance lesser than 2, while just 3\% of the questions have variance between 2 and 11. This result indicates that just a few principal components concentrates the most significative information and motivates the evaluation regarding the relationship between the principal components and the iGovTI classification.

@@

Finally, we select the two largest eigenvalues and their correspondent componets in order to evaluate the relationship between the iGovTI classification for 349 organizations and the two most informative variables. The Figure \ref{fig:ch2_fig3} shows the scatter diagram that plots the organizations with higher iGovTI with larger circunferences and colors near of red, while organizations with lower iGovTI have colors near of blue and shorter circunferences. It is possible to observe that organizations with higher iGovTI are concentrated in the top left quadrant, with a visual separation of organizations with lower iGovTI, but without a clear distance separating the classes.

@@

The visual discriminant analysis indicates that just a few principal components concentrates the most significative information and that the two principal components show a visual classification of organizations according to iGovTI classification, however it is not clear what are the CSF.

@@

RFE requires a classifier or predictor to evaluate its generalization performance by recursivelly removing the least significant features whose deletion will have the least effect on training errors, according to the higher variance measured from the features. We perform an algorithm evaluation in order to identify the classifier with the highest accuracy for iGovTI classification. The evaluated dataset is composed of 201 questions (features) and 349 organizations (observations), where each organization is classified according to iGovTI classes, which are initial, intermediate and enhanced. We divide the dataset into train and test, with the training data equivalent to 90\% of the whole dataset, while the test has 10 \% of the whole dataset.

The Table \ref{tab:ch2_tab1} present the selected classification algoritms and the measured accuracy for iGovTI classification. According to results, SVM \cite{hearst1998support} is the algorithm with highest classification accuracy, with 91.42\%, while the second is Elastic Net \cite{zou2005regularization}, with 83.15\% of accuracy. The results for iGovTI classification corroborates previous evaluations that highlight the advantages of SVM for classifications from small datasets \cite{guyon2002gene}. Additionally, our results indicate that SVM is the best classifier for RFE, which corroborates the previous research of Guyon \emph{et al} \cite{guyon2002gene}, where is proposed SVM-RFE, that is a method of gene selection utilizing SVM methods based on RFE.

@@

The next step is to use the selected algorithm as validator for recursive feature elimination in order to identify the CSF for iGovTI. Additionally, the RFE algorithm requires the number of desired most significatives features. We adopt 54 for this variable, considering that is the number of CSF identified by Ramos \emph{et al} \cite{ramos2016information} in a qualitative analysis, that is the proposed target to validate the results of the CSF identification for iGovTI.

The RFE algorith presents an ranking according to the significance of each feature, with an accuracy of 69,9\% for CSF classification when compared to the CSF identified by Ramos \emph{et al} \cite{ramos2016information} in a qualitative analysis.

@@

The proposed approach is evaluated and the experimental results show that the visual discriminant analysis, throught PCA, highlights important characteristcs of the data, and that a selected classifier and RFE can be applied for iGovTI classification and for CSF identification.

@@

Finally, SVM is used to select the more significant features identified by RFE, wich are 69,9\% similar to CSFs previsously identified by a qualitative analysis of the same datased.

>>>>

\chapter{Critical Success Factor Analysis Based on Feature Selection}
\label{apx:b_csf_fs}

Critical Success Factor (CSF) is a management term for an element that is necessary for an organization or project to achieve its mission. CSFs represent the principal assets or areas that must be given investments to achieve better results. CSF analysis is one challenger strategic management tool, which can provide a robust and very practical assessment for strategic planners.

The identification of the most significant information for one problem is referred to as feature selection by the signal processing and data mining areas, as well as it can be formulated as a principal component problem, which is a widely adopted signal processing technique for data visualization and feature extraction. Feature selection aims to select a subset of relevant information from a larger dataset, in order to improve: data visualization and data understanding, storage requirements, dimensionality, processing time, discriminative sensing, and to overcome overfitting problems to improve prediction and classification performance \cite{chandrashekar2014survey}.

Recursive Feature Elimination (RFE) is a feature selection method for small sample classification problems. RFE seeks to improve generalization performance by recursively removing the least significant features whose deletion will have the least effect on training errors, according to the higher variance measured from the features \cite{chen2007enhanced}.

We propose a critical factors analysis based on Principal Component Analysis (PCA) for visual discriminant analysis and based on RFE combined with Support Vector Machine (SVM) \cite{hearst1998support}, applied to the survey that evaluates the IT governance of Brazilian public organizations, in order to identify the CSF for IT governance of the public sector according to TCU. Results show how PCA can make the data discriminative and that SVM is the classifier that best performs and obtains an accuracy of 91.42\% to learn and classify according to TCU's IT governance evaluation of Brazilian public sector. Finally, SVM is used to highlight the more significant features identified by RFE, which are similar to CSFs previously identified by a qualitative analysis of the same dataset.

@@

The Brazilian Federal Court of Accounts (TCU, in Portuguese) surveys data regarding IT practices of Brazilian public organizations in order to audit IT governance. The dataset with a consolidate view about the answers for this survey the IT governance index is called iGovTI. The iGovTI is composed by 201 multiple choice questions, used for ranking according to their IT governance, submitted to 349 organizations. The TCU computes the IT governance index and classifies the IT governance of each organization. Additionally, Ramos \emph{et al} \cite{ramos2016information} classifies each question regarding its relevance for IT governance through a qualitative analysis, and identify the CSFs for selected IT managers regarding IT governance.

@@

PCA is a statistical technique commonly used for signal denoising, blind source separation, data compression, data visualization, feature extraction and dimensionality reduction, where a reduced number of features is extracted retaining as much information as possible \cite{jolliffe1986principal}. It uses an orthogonal transformation to convert a set of correlated variables into a set of linearly uncorrelated variables, where the first principal components have the largest variance.

PCA is an orthogonal basis transformation into new basis, by diagonalizing the centered covariance matrix of a data set \{$\mathbf{x}_j \in \mathbb{R}^m, j = 1, ... ,n$\}, defined by $\mathbf{C} = \frac{\mathbf{X}^\intercal\mathbf{X}}{n}$, where $\mathbf{X} = (\mathbf{x}_1, ... , \mathbf{x}_n)^\intercal$ and the samples are assumed to have zero mean. The eigenvectors $\mathbf{v}_i$ of $\mathbf{C}$ are called principal components (PC), and the sample variance along $\mathbf{v}_i$ of $\mathbf{C}$ is given by the corresponding eigenvalue $\lambda_i$. Projecting onto the eigenvectors with the largest eigenvalues assumes that minimal information is lost, considering that in many applications these directions contain the most interesting information, such as in in data compression and denoising.

Initially, we compute the covariance matrix $\mathbf{C}$ of a zero mean data and visualize the data relationship for the sample covariance. Sample covariance is calculated by computing deviations of each measurement from the average of all measurements for that variable. Then the deviations for the two measurements are multiplied together separately for each subject. Finally these values are averaged. After that, the eigenvectors $\mathbf{v}_i$ and eigenvalues $\lambda_i$ of $\mathbf{C}$ are computed through Singular Value Decomposition (SVD), then it is possible to evaluate the variance distribution of the extracted components through an empirical cumulative distribution function (ECDF). Evaluating the variance distribution we expect to visualize if some features concentrates the variance and indicates advantages for dimensionality reduction.

@@

Feature selection aims the identification of the most significant information for one problem or algorithm, such as classification or prediction problems. RFE is a feature selection method for small sample classification problems by recursively removing the least significant features whose deletion will have the least effect on training errors, according to the higher variance measured from the features through a selected classifier.

Initially, it is necessary to identify one classifier that can identify the iGovTI classification of one organization according to a training dataset. Therefore, we propose an algorithm evaluation in order to identify which one presents the best accuracy for iGovTI classification. The selected algorithm should be used by RFE to identify the CSF, that should be compared to results of the CSF qualitative analysis conducted by Ramos \emph{et al} \cite{ramos2016information}.

Feature selection doesn't combine attributes, as PCA, but just evaluates their informative quality, predictive power and select the best set. Given an external estimator or classifier, that assigns weights to features, RFE is able to select features by recursively considering smaller and smaller sets of features. First, the estimator is trained on the initial set of features and the importance of each feature is obtained either through a coefficient attribute or through a feature importances attribute. Then, the least important features are pruned from current set of features. That procedure is recursively repeated on the pruned set until the desired number of features to select is eventually reached. RFE can also rank all features according to when they were eliminated.

@@

In this section we present the experiments and results for the visual discriminant analysis based on PCA and for CSF analysis based on RFE, and discuss the results.

For the visual discriminant analysis we initially we compute the zero mean and the the covariance matrix $\mathbf{C}$ is computed from $\mathbf{X}$.The results are shown by Figure \ref{fig:ch2_fig1}.

@@

In the next step the eigenvectors $\mathbf{v}_i$ and eigenvalues $\lambda_i$ of $\mathbf{C}$ are computed through SVD. Considering that the first principal components have the largest variance indicated by their eigenvalues, it is necessary to evaluate the variance distribution of the measured eigenvalues. Therefore, we present the Figure \ref{fig:ch2_fig2}, wich shows the variance ECDF of the iGovTI questions and shows that 97\% of the questions have variance lesser than 2, while just 3\% of the questions have variance between 2 and 11. This result indicates that just a few principal components concentrates the most significant information and motivates the evaluation regarding the relationship between the principal components and the iGovTI classification.

@@

Finally, we select the two largest eigenvalues and their correspondent components in order to evaluate the relationship between the iGovTI classification for 349 organizations and the two most informative variables. The Figure \ref{fig:ch2_fig3} shows the scatter diagram that plots the organizations with higher iGovTI with larger circumferences and colors near of red, while organizations with lower iGovTI have colors near of blue and shorter circumferences. It is possible to observe that organizations with higher iGovTI are concentrated in the top left quadrant, with a visual separation of organizations with lower iGovTI, but without a clear distance separating the classes.

@@

The visual discriminant analysis indicates that just a few principal components concentrates the most significant information and that the two principal components show a visual classification of organizations according to iGovTI classification, however it is not clear what are the CSF.

@@

RFE requires a classifier or predictor to evaluate its generalization performance by recursively removing the least significant features whose deletion will have the least effect on training errors, according to the higher variance measured from the features. We perform an algorithm evaluation in order to identify the classifier with the highest accuracy for iGovTI classification. The evaluated dataset is composed of 201 questions (features) and 349 organizations (observations), where each organization is classified according to iGovTI classes, which are initial, intermediate and enhanced. We divide the dataset into train and test, with the training data equivalent to 90\% of the whole dataset, while the test has 10 \% of the whole dataset.

The Table \ref{tab:ch2_tab1} present the selected classification algorithms and the measured accuracy for iGovTI classification. According to results, SVM \cite{hearst1998support} is the algorithm with highest classification accuracy, with 91.42\%, while the second is Elastic Net \cite{zou2005regularization}, with 83.15\% of accuracy. The results for iGovTI classification corroborates previous evaluations that highlight the advantages of SVM for classifications from small datasets \cite{guyon2002gene}. Additionally, our results indicate that SVM is the best classifier for RFE, which corroborates the previous research of Guyon \emph{et al} \cite{guyon2002gene}, where is proposed SVM-RFE, that is a method of gene selection utilizing SVM methods based on RFE.

@@

The next step is to use the selected algorithm as validator for recursive feature elimination in order to identify the CSF for iGovTI. Additionally, the RFE algorithm requires the number of desired most significants features. We adopt 54 for this variable, considering that is the number of CSF identified by Ramos \emph{et al} \cite{ramos2016information} in a qualitative analysis, that is the proposed target to validate the results of the CSF identification for iGovTI.

The RFE algorithm presents an ranking according to the significance of each feature, with an accuracy of 69,9\% for CSF classification when compared to the CSF identified by Ramos \emph{et al} \cite{ramos2016information} in a qualitative analysis.

@@

The proposed approach is evaluated and the experimental results show that the visual discriminant analysis, through PCA, highlights important characteristics of the data, and that a selected classifier and RFE can be applied for iGovTI classification and for CSF identification.

@@

Finally, SVM is used to select the more significant features identified by RFE, which are 69,9\% similar to CSFs previously identified by a qualitative analysis of the same dataset.
